---
title: "iterations, list columns"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(p8105.datasets)

```

Set seed for reproducibility

```{r}
set.seed(12345)
```


```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
l = 
  list(
    vec_numeric = 1:5,
    vec_char = LETTERS,
    matrix = matrix(1:10, nrow = 5, ncol = 2),
    summary = summary(rnorm(100))
  )
```

Accessing lists

```{r}
l$vec_char
l[[2]]
l[["summary"]]
```

### Loops

```{r}
list_norm_samples = 
  list(
    a = rnorm(20, 1, 5),
    b = rnorm(20, 0, 7),
    c = rnorm(20, 20, 1),
    d = rnorm(20, -45, 13)
  )
```
Function from last class
```{r}
mean_and_sd = function(x) {
  
    if(!is.numeric(x)) {
    stop("Argument x should be numeric")} 
  else if (length(x) < 2) {
    stop("Cannot be computed for length 1 vectors")}
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Hard to apply a funciton to many inputs ion a list without getting disorganized

```{r}
mean_and_sd(list_norm_samples$a)
mean_and_sd(list_norm_samples$b)
mean_and_sd(list_norm_samples$c)
mean_and_sd(list_norm_samples$d)
```

Creating a For Loop, i is the variable for different interchaning inputs
```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm_samples[[i]])
  
}
```


### use `map`

```{r}

output2 = map(list_norm_samples, mean_and_sd)

#the map function can do a variety of outputs
output_median = map(list_norm_samples, median)
output_summary = map(list_norm_samples, summary)
```

### Create DF

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norm_samples
  )
```

```{r}
listcol_df |> pull(samp)

map(listcol_df$samp, mean_and_sd)

listcol_df |> 
  mutate(
    mean_sd = map(samp, mean_and_sd),
    meidan = map(samp, median)) |> 
  select(name, mean_sd)
```

Function from last class

```{r}
 nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

nsduh_import = function(html, table_number, outcome_name) {
  
  html = 
  nsduh_html |> 
  html_table() |> 
  nth(table_number) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent),
    outcome = outcome_name) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

nsduh_import(nsduh_html, 1, "marj")
nsduh_import(nsduh_htm, 4, "cocaine")
nsduh_import(nsduh_htm, 5, "heroine")

```

Import Data using a For Loop

```{r}
table_input = list(1, 4, 5)
name_input = list("marj", "cocaine", "heroin")

output = vector("list", length = 3)

for(i in c(1:3)) {
  
  output[[i]] = (nsduh_import(msduh_html, table_input[[i]], name_input[[i]]))

  }

nsduh_df = bind_rows(output)
nsduh_df
```


Lets try again using MAP Statement

```{r}
 nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

nsduh_import = function(html, table_number) {
  
  html = 
  nsduh_html |> 
  html_table() |> 
  nth(table_number) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

nsduh_df =
  tibble(
    name = c("marj", "cocaine", "heroin"),
    number = c(1, 4, 5)
  ) |> 
  mutate(
    table = map(number, nsduh_import, html = nsduh_html)) |> 
  unnest(table)

#map(nsduh_df$number, nsduh_import, html = nsduh_html)
```

Returning to the Weather Data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USW00022534 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

```{r}
weather_nest = weather_df |> 
  nest(df = date:tmin)
```

Can I Regress Tmax and Tmin for Each of these

```{r}
central_park_df =
  weather_nest |> 
  pull(df) |> 
  nth(1)

central_park_df
```

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
weather_lm(central_park_df)
```

lets try a for loop

```{r}
input_list = weather_nest |> pull(df)

output = vector("list", length = 3)

for (i in 1:3) {
  output[[i]] = weather_lm(input_list[[i]])
}

weather_nest |> 
  mutate(models = map(df, weather_lm))
```

