---
title: "writing functions"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(p8105.datasets)

```

Set seed for reproducibility

```{r}
set.seed(12345)
```


### Z Score Function

z scores subtract the mean and divide by the standard deviation

```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```

Basic Compute Z scores for `x_vec`

```{r}
(x_vec - mean(x_vec))/sd(x_vec)
```


Write a function to do this

```{r}
z_score = function(x) {
  
  if(!is.numeric(x)) {
    stop("Argument x should be numeric")} 
  else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")}
  z = ((x - mean(x))/sd(x))
  
  z
}
```

Check that this works

```{r}
z_score(x = x_vec)

z_score(x = rnorm(10, mean = 5))
```
Keep checking
```{r eval = FALSE}
z_score(x = 3)

z_score(c("hello", "there"))

z_score(c(TRUE, TRUE, FALSE, TRUE))

z_score(iris)
```


## Multiple Outputs

Write a function that returns the mean and sd from a sample of numbers


```{r}
mean_and_sd = function(x) {
  
    if(!is.numeric(x)) {
    stop("Argument x should be numeric")} 
  else if (length(x) < 2) {
    stop("Cannot be computed for length 1 vectors")}
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Double check

```{r}
mean_and_sd(x= x_vec)
```


### Start getting means and sds

```{r}
x_vec = rnorm(n = 30, mean = 5, sd = 0.5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Create a function that uses 'n' a true mean, and true SD as inputs

```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
  
}

sim_mean_sd(n_obs = 3000, mu = 50, sigma = 5)
```
### How can we write a function for this old code?

fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") |>
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") |>
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") |>
  mutate(movie = "return_king")

lotr_tidy = bind_rows(fellowship_ring, two_towers, return_king) |>
  janitor::clean_names() |>
  gather(key = sex, value = words, female:male) |>
  mutate(race = str_to_lower(race)) |> 
  select(movie, everything()) 


```{r}
lotr_load_tidy = function(path = "data/LotR_Words.xlsx", cell_range, movie_name) {
  
  movie_df = 
    readxl::read_excel(path, range = cell_range) |> 
    mutate(movie = movie_name) |> 
    janitor::clean_names() |> 
    pivot_longer(
      female:male,
      names_to = "sex",
      values_to = "words"
    ) |> 
    select(movie, everything())
  
  movie_df
}


lotr_df = 
bind_rows(
  lotr_load_tidy(cell_range = "B3:D6", movie_name = "fellowship_ring"),
  lotr_load_tidy(cell_range = "F3:H6", movie_name = "two_towers"),
  lotr_load_tidy(cell_range = "J3:L6", movie_name = "return_king")
  )

lotr_df

```
Old Reading Code from web Drug Use

nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

data_marj = 
  nsduh_html |> 
  html_table() |> 
  nth(1) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))

Try to write a quick function.

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

nsduh_import = function(html, table_number, outcome_name) {
  
  html = 
  nsduh_html |> 
  html_table() |> 
  nth(table_number) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent),
    outcome = outcome_name) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
}

marj_df = nsduh_import(html = nsduh_html, table_number = 1, outcome_name = "Marijuana Use")

marj_df 



```



