---
title: "writing functions"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(p8105.datasets)

```

Set seed for reproducibility

```{r}
set.seed(12345)
```


### Z Score Function

z scores subtract the mean and divide by the standard deviation

```{r}
x_vec = rnorm(20, mean = 5, sd = .3)
```

Basic Compute Z scores for `x_vec`

```{r}
(x_vec - mean(x_vec))/sd(x_vec)
```


Write a function to do this

```{r}
z_score = function(x) {
  
  if(!is.numeric(x)) {
    stop("Argument x should be numeric")} 
  else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")}
  z = ((x - mean(x))/sd(x))
  
  z
}
```

Check that this works

```{r}
z_score(x = x_vec)

z_score(x = rnorm(10, mean = 5))
```
Keep checking
```{r eval = FALSE}
z_score(x = 3)

z_score(c("hello", "there"))

z_score(c(TRUE, TRUE, FALSE, TRUE))

z_score(iris)
```


## Multiple Outputs

Write a function that returns the mean and sd from a sample of numbers


```{r}
mean_and_sd = function(x) {
  
    if(!is.numeric(x)) {
    stop("Argument x should be numeric")} 
  else if (length(x) < 2) {
    stop("Cannot be computed for length 1 vectors")}
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Double check

```{r}
mean_and_sd(x= x_vec)
```


### Start getting means and sds

```{r}
x_vec = rnorm(n = 30, mean = 5, sd = 0.5)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
```

Create a function that uses 'n' a true mean, and true SD as inputs

```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

tibble(
  mean = mean(x_vec),
  sd = sd(x_vec)
)
  
}

sim_mean_sd(n_obs = 3000, mu = 50, sigma = 5)
```

